\section{Drone applications}
The use of drones in the industry and business has evolved a lot in the last few years, and the use evolves more each year. 
The industries where drones are mostly used today are farming and military.
\newline
The use of drones in farming has evolved the traditional way of farming, as the drone can do things the farmer cannot do himself. The drones, that are most used for farming, is multirotor drones. The drones can scan a whole field in minutes, and obtain knowledge of the crop's health. 
\newline
\newline
The military has used drones since 1955, mainly for things where it is too dangerous for soldiers. This includes both combat missions and supervision. The military mostly use fixed wing drones because they are bigger and can carry a bigger cargo. They are also much more efficient, and therefore have a much longer fly time. The fixed wing drone comes in all sizes, from small hand launched drones to large planes.
\newline
\newline
It is not only in the farming industry and military drones have been used, or are being used.
Drones is also being used for delivery of food and medicine to places where humans cannot get to. Such as areas where natural disasters have appeared, where the drones can give air support to the area \cite{drones_in_generel}.
\newline
In the future drones would be used to a lot more tasks, for example the multirotor drone will be used for exploration of mines and crash sites. Thus drones have to work in small and narrow places, where they always have to know if it can fit. The multirotor drone will be used for this because it has a better mobility, than a fixed wing drone which needs a bigger space to fly.